---
title: "Group Prosociality with OT"
output: word_document
date: "2022-09-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Install your Packages}
#install.packages("rstudioapi")
#install.packages("openxlsx")
#install.packages("dplyr")
#install.packages("tidyr")
#install.packages("tidyverse")
#install.packages("pscl")
#install.packages("multcomp")
#install.packages("lsmeans")
#install.packages("fitdistrplus")
#install.packages("glmmTMB")
#install.packages("overdisp")
#install.packages("sjPlot")
#install.packages("Rmisc")
#install.packages("rstatix")
#install.packages("MASS")
#install.packages("gridExtra")
#install.packages("grid")
#install.packages("gridtext")

```

```{r Library your Packages}
library(rstudioapi)
library(openxlsx)
library(readxl)
library(dplyr)
library(plyr)
library(tidyr)
library(tidyverse)
library(pscl)
library(multcomp)
library(emmeans)
library(lsmeans)
library(fitdistrplus)
library(lme4)
library(car)
library(glmmTMB)
library(emmeans)
library(overdisp)
library(sjPlot)
library(Rmisc)
library(rstatix)
library(MASS)
library(gridExtra)
library(grid)
library(gridtext)

```


```{r Read the Data File}

model2.data <- read_excel("C:/Users/matth/OneDrive/Documents/Georgia State/Research Projects/Group Prosociality/Data Collection and Schedule/Final Results and Final R Code/Model_2_Data_Frame.xlsx")

```

```{r Clean the Data Frames}

model2.data$OT <- ifelse(model2.data$fur_rubbing == 1, 1, ifelse(model2.data$grooming == 1, 1, 0))


model2.data$subject <- as.factor(model2.data$subject)
model2.data$group <- as.factor(model2.data$group)
model2.data$training <- as.factor(model2.data$training)
model2.data$block <- as.numeric(model2.data$block)
model2.data$date <- as.Date(model2.data$date, format = "%m/%d/%Y", optional = TRUE)
model2.data$session_number <- as.numeric(model2.data$session_number)
model2.data$session_type <- as.factor(model2.data$session_type)
model2.data$OT <- as.factor(model2.data$OT)
model2.data$recipient <- as.factor(model2.data$recipient)
model2.data$csi <- as.numeric(model2.data$csi)
model2.data$related <- as.factor(model2.data$related)
model2.data$total_pull <- as.numeric(model2.data$total_pull)
model2.data$total_prosocial <- as.numeric(model2.data$total_prosocial)
model2.data$indiv_pull <- as.numeric(model2.data$indiv_pull)
model2.data$indiv_run <- as.numeric(model2.data$indiv_run)
model2.data$indiv_agg <- as.numeric(model2.data$indiv_agg)
model2.data$total_run <- as.numeric(model2.data$total_run)
model2.data$total_aggression <- as.numeric(model2.data$total_aggression)



levels(model2.data$subject)
class(model2.data$date)
levels(model2.data$session_type)
levels(model2.data$OT)
levels(model2.data$training)
levels(model2.data$recipient)

```

```{r Merge with demographics}
demographics <- read_excel("C:/Users/matth/OneDrive/Documents/Georgia State/Research Projects/Group Prosociality/Data Collection and Schedule/Final Results and Final R Code/Monkey_Demographics.xlsx")

merged.data <- merge(x = demographics, y = model2.data, by.x = "subject", by.y = "subject")
nrow(merged.data) == nrow(merged.data)
head(merged.data)

merged.data <- arrange(merged.data, group, session_number, subject)
head(merged.data)

merged.data$sex <- as.factor(merged.data$sex)
merged.data$age <- as.numeric(merged.data$age)
merged.data$rank <- as.numeric(merged.data$rank)
merged.data$recipient_rank <- as.numeric(merged.data$recipient_rank)
merged.data$relative_rank <- as.factor(merged.data$relative_rank)
merged.data$rank_score <- as.numeric(merged.data$rank_score)

merged.data$rank_diff <- merged.data$rank - merged.data$recipient_rank

# Create a back up that is sorted how you like it
summary.data <- model2.data
# Move on with the merged data file
model2.data <- merged.data
rm(merged.data)

model2.data$subject <- as.factor(model2.data$subject)
levels(model2.data$subject)
```

```{r Make a Data Frame for each Group}
griffin.data <- subset(model2.data, group == "griffin")
logan.data <- subset(model2.data, group == "logan")
nkima.data <- subset(model2.data, group == "nkima")
mason.data <- subset(model2.data, group == "mason")
```


```{r For Model 2, we are only focused on the Accessible (Exp) Sessions}
accessible.data <- subset(model2.data, session_type == "Accessible")
summary(accessible.data$session_type)
```

##From MSc Model 1 [FINAL].RMD

Total Pulls in the Accessible Sessions: 4933

Total Pulls with at least 1 recipient: 3388

Total Pulls with no recipient: 1523

##From MSc Model 3 [FINAL].RMD

Total Pulls followed by a Run: 2562

Total Pulls followed by an Aggression: 103


```{r Descriptive Statistics of Pulls and Recipients}
# Total number of individual receives
sum(accessible.data$indiv_pull)

summary(accessible.data$indiv_pull)

# Average amount of pulls per OT Condition
summarySE(accessible.data, measurevar="indiv_pull", groupvars=c("OT"))

# This tells us who the recipient of most of the pulls was (This includes recipient and in proximity)
ddply(accessible.data, ~ recipient, summarise, receiving_sum=sum(indiv_pull, na.rm = TRUE))
# This breaks this down into each group so percentages can easily be calculated
ddply(griffin.data, ~ recipient, summarise, receiving_sum=sum(indiv_pull, na.rm = TRUE))
ddply(logan.data, ~ recipient, summarise, receiving_sum=sum(indiv_pull, na.rm = TRUE))
ddply(nkima.data, ~ recipient, summarise, receiving_sum=sum(indiv_pull, na.rm = TRUE))
ddply(mason.data, ~ recipient, summarise, receiving_sum=sum(indiv_pull, na.rm = TRUE))



```

```{r Visualize Pulls by CSI}
summary(accessible.data$csi)

view_df(accessible.data, show.frq = T, show.prc = T, show.na = T)

df<-summarySE(accessible.data, measurevar="indiv_pull", groupvars=c("subject", "recipient"))
df

accessible.data.visual <- accessible.data
```


```{r Visualize Pulls by CSI}
accessible.data.visual$subject <- as.factor(accessible.data.visual$subject)
levels(accessible.data.visual$subject)

griffin.visual <- subset(accessible.data.visual, group == "griffin")
logan.visual <- subset(accessible.data.visual, group == "logan")
mason.visual <- subset(accessible.data.visual, group == "mason")
nkima.visual <- subset(accessible.data.visual, group == "nkima")

Logan_CSI <- ggplot(logan.visual, aes(x = csi, y = indiv_pull, fill = OT)) +
              geom_point(size = 3.0, position = position_dodge(width = 0.1), pch = 21, color = "black") +
              geom_smooth(aes(color = OT), method = glm, se = FALSE, fullrange = FALSE, level = 0.95) +
              xlab("Composite Sociality Index (CSI)") +
              ylab("Number of Pulls per Session") +
              ylim(0, 65) +
              xlim(0, 5) +
              labs(title = "Group 1 (n = 6)") +
              geom_vline(xintercept = 1, linetype = "dashed", color = "black") +
              #facet_wrap(~subject) +
              #facet_wrap(~ factor(group, 
              #                    labels = c("(a) Griffin", "(b) Logan", "(c) Mason", "(d) Nkima")),
              #                    ncol=2) +
              theme_bw() +
              scale_fill_manual(values = c("gray69", "blue2")) +
              scale_color_manual(values = c("gray69", "blue2")) +
              annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf) +
              annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
              theme(panel.grid.major.x = element_blank(),
                    panel.grid.minor.x = element_blank(),
                    #axis.title = element_blank(),
                    legend.position = "none",
                    plot.title = element_text(hjust = 0.5),
                    panel.grid.major.y = element_blank(),
                    panel.grid.minor.y = element_blank())


Griffin_CSI <- ggplot(griffin.visual, aes(x = csi, y = indiv_pull, fill = OT)) +
              geom_point(size = 3.0, position = position_dodge(width = 0.1), pch = 21, color = "black") +
              geom_smooth(aes(color = OT), method = glm, se = FALSE, fullrange = FALSE, level = 0.95) +
              xlab("Composite Sociality Index (CSI)") +
              ylab("Lever Presses per Session") +
              #ylim(0, 65) +
              xlim(0, 5) +
              labs(title = "Group 2 (n = 5)") +
              geom_vline(xintercept = 1, linetype = "dashed", color = "black") +
              #facet_wrap(~subject) +
              #facet_wrap(~ factor(group, 
              #                    labels = c("(a) Griffin", "(b) Logan", "(c) Mason", "(d) Nkima")),
              #                    ncol=2) +
              theme_bw() +
              scale_fill_manual(values = c("gray69", "blue2"), labels = c('0' = "No OT", "1" = "+ OT")) +
              scale_color_manual(values = c("gray69", "blue2"), labels = c('0' = "No OT", "1" = "+ OT")) +
              annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf) +
              annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
              theme(panel.grid.major.x = element_blank(),
                    panel.grid.minor.x = element_blank(),
                    #axis.title = element_blank(),
                    legend.position = c(0.85, 0.75),
                    legend.title = element_blank(),
                    plot.title = element_text(hjust = 0.5),
                    panel.grid.major.y = element_blank(),
                    panel.grid.minor.y = element_blank())


Nkima_CSI <- ggplot(nkima.visual, aes(x = csi, y = indiv_pull, fill = OT)) +
              geom_point(size = 3.0, position = position_dodge(width = 0.1), pch = 21, color = "black") +
              geom_smooth(aes(color = OT), method = glm, se = FALSE, fullrange = FALSE, level = 0.95) +
              xlab("Composite Sociality Index (CSI)") +
              ylab("Lever Presses per Session") +
              ylim(0, 65) +
              xlim(0, 5) +
              #facet_wrap(~subject) +
              #facet_wrap(~ factor(group, 
              #                    labels = c("(a) Griffin", "(b) Logan", "(c) Mason", "(d) Nkima")),
              #                    ncol=2) +
              labs(title = "Group 3 (n = 4)") +
              geom_vline(xintercept = 1, linetype = "dashed", color = "black") +
              theme_bw() +
              scale_fill_manual(values = c("gray69", "blue2")) +
              scale_color_manual(values = c("gray69", "blue2")) +
              annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf) +
              annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
              theme(panel.grid.major.x = element_blank(),
                    panel.grid.minor.x = element_blank(),
                    #axis.title = element_blank(),
                    legend.position = "none",
                    plot.title = element_text(hjust = 0.5),
                    panel.grid.major.y = element_blank(),
                    panel.grid.minor.y = element_blank())

Mason_CSI <- ggplot(mason.visual, aes(x = csi, y = indiv_pull, fill = OT)) +
              geom_point(size = 3.0, position = position_dodge(width = 0.1), pch = 21, color = "black") +
              geom_smooth(aes(color = OT), method = glm, se = FALSE, fullrange = FALSE, level = 0.95) +
              xlab("Composite Sociality Index (CSI)") +
              ylab("Lever Presses per Session") +
              ylim(0, 65) +
              xlim(0, 5) +
              #facet_wrap(~subject) +
              #facet_wrap(~ factor(group, 
              #                    labels = c("(a) Griffin", "(b) Logan", "(c) Mason", "(d) Nkima")),
              #                    ncol=2) +
              labs(title = "Group 4 (n = 8)") +
              geom_vline(xintercept = 1, linetype = "dashed", color = "black") +
              theme_bw() +
              scale_fill_manual(values = c("gray69", "blue2")) +
              scale_color_manual(values = c("gray69", "blue2")) +
              annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf) +
              annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
              theme(panel.grid.major.x = element_blank(),
                    panel.grid.minor.x = element_blank(),
                    #axis.title = element_blank(),
                    legend.position = "none",
                    plot.title = element_text(hjust = 0.5),
                    panel.grid.major.y = element_blank(),
                    panel.grid.minor.y = element_blank())


yaxis <- textGrob("Lever Presses per Session", rot = 90, gp = gpar(fontsize = 20))
bottom <- textGrob("Composite Sociality Index (CSI)", gp = gpar(fontsize = 20))


g_csi<-grid.arrange(Logan_CSI, Griffin_CSI, Nkima_CSI, Mason_CSI, 
                nrow = 2)

#g<-grid.arrange(Logan_CSI, Griffin_CSI, Nkima_CSI, Mason_CSI, 
#                nrow = 2, bottom = bottom, left = yaxis)

ggsave("CSI_Graph_NEW.png", g_csi, height = 6, width = 10, units = "in")

```

```{r}
Total_CSI <- ggplot(accessible.data.visual, aes(x = csi, y = indiv_pull, fill = OT)) +
              geom_point(size = 3.0, position = position_dodge(width = 0.1), pch = 21, color = "black") +
              geom_smooth(aes(color = OT), method = glm, se = FALSE, fullrange = FALSE, level = 0.95) +
              xlab("Composite Sociality Index (CSI)") +
              ylab("Lever Presses per Session") +
              ylim(0, 65) +
              xlim(0, 5) +
              #facet_wrap(~subject) +
              #facet_wrap(~ factor(group, 
              #                    labels = c("(a) Griffin", "(b) Logan", "(c) Mason", "(d) Nkima")),
              #                    ncol=2) +
              labs(title = "All Groups (n = 23)") +
              geom_vline(xintercept = 1, linetype = "dashed", color = "red", linewidth = 2) +
              theme_bw() +
              scale_fill_manual(values = c("gray69", "blue2")) +
              scale_color_manual(values = c("gray69", "blue2")) +
              annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf) +
              annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
              theme(panel.grid.major.x = element_blank(),
                    panel.grid.minor.x = element_blank(),
                    plot.title = element_text(hjust = 0.5),
                    panel.grid.major.y = element_blank(),
                    panel.grid.minor.y = element_blank(),
                    axis.title.x = element_text(size = 16),
                    axis.title.y = element_text(size = 16),
                    axis.text.x = element_text(size = 14),
                    axis.text.y = element_text(size = 14),
                    legend.position = c(0.90, 0.80),
                    legend.title = element_blank(),
                    legend.text = element_text(size = 12),
                    legend.key.size = unit(1.0, "cm"))
Total_CSI

ggsave("CSI_Graph_No_Group.png", height = 5, width = 8, units = "in")
```


```{r Pulls by Rank Difference instead of Rank ELO Rating}
griffin.visual.rank <- subset(accessible.data, group == "griffin")
logan.visual.rank <- subset(accessible.data, group == "logan")
mason.visual.rank <- subset(accessible.data, group == "mason")
nkima.visual.rank <- subset(accessible.data, group == "nkima")

logan_rank <- ggplot(logan.visual.rank, 
                        aes(x = rank_diff, y = indiv_pull)) +
                  geom_point(size = 3.0, pch = 21, color = "black", fill = "green4") +
                  labs(title = "Group 1 (n = 6)", 
                       x = "Rank Difference of Subject and Recipient", y = "Lever Presses per Session") +
                  theme_bw() +
                  ylim(0, 80) +
                  xlim(-500, 500) +
                  geom_vline(xintercept = 0, linetype = "dashed") +
                  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf) +
                  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
                  scale_fill_manual(values = c("gray69", "blue2")) +
                  scale_color_manual(values = c("gray69", "blue2")) +
                  theme(legend.position = "none",
                        panel.grid.minor.x = element_blank(),
                        panel.grid.major.x = element_blank(),
                        plot.title = element_text(hjust = 0.5),
                        panel.grid.major.y = element_blank(),
                        panel.grid.minor.y = element_blank(),
                        axis.title.x = element_text(size = 16),
                        axis.title.y = element_text(size = 16))

griffin_rank <- ggplot(griffin.visual.rank, 
                        aes(x = rank_diff, y = indiv_pull)) +
                  geom_point(size = 3.0, pch = 21, color = "black", fill = "green4") +
                  labs(title = "Group 2 (n = 5)", 
                       x = "Rank Difference of Subject and Recipient", y = "Lever Presses per Session") +
                  theme_bw() +
                  ylim(0, 80) +
                  xlim(-500, 500) +
                  geom_vline(xintercept = 0, linetype = "dashed") +
                  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf) +
                  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
                  scale_fill_manual(values = c("gray69", "blue2")) +
                  scale_color_manual(values = c("gray69", "blue2")) +
                  theme(legend.position = "none",
                        panel.grid.minor.x = element_blank(),
                        panel.grid.major.x = element_blank(),
                        plot.title = element_text(hjust = 0.5),
                        panel.grid.major.y = element_blank(),
                        panel.grid.minor.y = element_blank(),
                        axis.title.x = element_text(size = 16),
                        axis.title.y = element_text(size = 16))

nkima_rank <- ggplot(nkima.visual.rank, 
                        aes(x = rank_diff, y = indiv_pull)) +
                  geom_point(size = 3.0, pch = 21, color = "black", fill = "green4") +
                  labs(title = "Group 3 (n = 4)", 
                       x = "Rank Difference of Subject and Recipient", y = "Lever Presses per Session") +
                  theme_bw() +
                  ylim(0, 80) +
                  xlim(-500, 500) +
                  geom_vline(xintercept = 0, linetype = "dashed") +
                  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf) +
                  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
                  scale_fill_manual(values = c("gray69", "blue2")) +
                  scale_color_manual(values = c("gray69", "blue2")) +
                  theme(legend.position = "none",
                        panel.grid.minor.x = element_blank(),
                        panel.grid.major.x = element_blank(),
                        plot.title = element_text(hjust = 0.5),
                        panel.grid.major.y = element_blank(),
                        panel.grid.minor.y = element_blank(),
                        axis.title.x = element_text(size = 16),
                        axis.title.y = element_text(size = 16))

mason_rank <- ggplot(mason.visual.rank, 
                        aes(x = rank_diff, y = indiv_pull)) +
                  geom_point(size = 3.0, pch = 21, color = "black", fill = "green4") +
                  labs(title = "Group 4 (n = 8)", 
                       x = "Rank Difference of Subject and Recipient", y = "Lever Presses per Session") +
                  theme_bw() +
                  ylim(0, 80) +
                  xlim(-500, 500) +
                  geom_vline(xintercept = 0, linetype = "dashed") +
                  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf) +
                  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
                  scale_fill_manual(values = c("gray69", "blue2")) +
                  scale_color_manual(values = c("gray69", "blue2")) +
                  theme(legend.position = "none",
                        panel.grid.minor.x = element_blank(),
                        panel.grid.major.x = element_blank(),
                        plot.title = element_text(hjust = 0.5),
                        panel.grid.major.y = element_blank(),
                        panel.grid.minor.y = element_blank(),
                        axis.title.x = element_text(size = 16),
                        axis.title.y = element_text(size = 16))


g_rankdiff<-grid.arrange(logan_rank, griffin_rank, nkima_rank, mason_rank, 
                nrow = 2)

ggsave("Rank_Diff_Graph_NEW.png", g_rankdiff, height = 7, width = 10, units = "in")
```
```{r}

rank_total_graph <- ggplot(accessible.data, 
                        aes(x = rank_diff, y = indiv_pull)) +
                  geom_point(size = 3.0, pch = 21, color = "black", fill = "green4") +
                  labs(title = "All Groups (n = 23)", 
                       x = "Rank Difference of Subject and Recipient", y = "Lever Presses per Session") +
                  theme_bw() +
                  ylim(0, 80) +
                  xlim(-500, 500) +
                  geom_vline(xintercept = 0, linetype = "dashed", color = "red", linewidth = 2) +
                  annotate("segment", x=-Inf, xend=Inf, y=-Inf, yend=-Inf) +
                  annotate("segment", x=-Inf, xend=-Inf, y=-Inf, yend=Inf) +
                  scale_fill_manual(values = c("gray69", "blue2")) +
                  scale_color_manual(values = c("gray69", "blue2")) +
                  theme(panel.grid.major.x = element_blank(),
                    panel.grid.minor.x = element_blank(),
                    plot.title = element_text(hjust = 0.5),
                    panel.grid.major.y = element_blank(),
                    panel.grid.minor.y = element_blank(),
                    axis.title.x = element_text(size = 16),
                    axis.title.y = element_text(size = 16),
                    axis.text.x = element_text(size = 14),
                    axis.text.y = element_text(size = 14),
                    legend.position = c(0.90, 0.80),
                    legend.title = element_blank(),
                    legend.text = element_text(size = 12),
                    legend.key.size = unit(1.0, "cm"))

rank_total_graph

ggsave("Rank_Graph_No_Group.png", height = 5, width = 8, units = "in")


```



```{r Check for Overdispersion}
# Overdispersino occurs when the VAriance of your DV is >>> Mean of your DV
var(accessible.data$indiv_pull)
mean(accessible.data$indiv_pull)

# Variance Ratio
var(accessible.data$indiv_pull)/mean(accessible.data$indiv_pull)
# Over dispersion = PRESENT!

```
Mean: 1.2
Variance: 23.9
Variance Ratio: 20.1

 OVERDISPERSION means we need Negative Binomial or Quasi-Poisson

```{r Correlation between CSI and Rank Difference}
# Correlation between CSI and Rank
accessible.data$rank_diff_abs <- abs(accessible.data$rank_diff)

ggplot(accessible.data, aes(x = rank_diff_abs, y = csi)) +
  geom_point() +
  geom_smooth(method = lm) +
  theme_classic()

cor.test(accessible.data$csi, accessible.data$rank_diff_abs, method = "pearson")
```

A Pearson correlation coefficient was computed to assess the linear relationship between CSI and Rank Difference. There was a significant negative correlation between the two variables, r(3538) = -0.422, p < 0.001. We were more interested in the differences associated with social closeness and therefore, we removed rank difference from the model.

```{r Check relations between CSI and Relatedness}

ggplot(accessible.data, aes(x = factor(related), y = csi)) +
  geom_point() +
  geom_abline(fullrange = FALSE) +
  theme_classic()

cor.test(accessible.data$csi, as.numeric(accessible.data$related), method = "pearson")
```
Using a Point-Biserial correlation, we determined that there was a significant positive correlation between CSI and relatedness such that related individuals were also socially closer r[PM](3538) = 0.373, p < 0.001.

```{r Test for Colinearity with VIF}
# Z-Center Numeric Predcitors
accessible.data$z.csi = as.vector(scale(accessible.data$csi))
accessible.data$z.session_number = as.vector(scale(accessible.data$session_number))
accessible.data$z.rank_diff_abs = as.vector(scale(accessible.data$rank_diff_abs))
hist(accessible.data$z.csi)

simple_model2 <- lm(as.numeric(indiv_pull) ~ OT + z.csi + z.session_number, data = accessible.data)

summary(simple_model2)

vif(simple_model2)

# ALL VIFs should be low, around 1.0 preferably; Above 2.5 is concerning
```

```{r Model 2: ZINB What factors influence prosocial pulls?}
# Negative Binomial Regression
ZINB_2 <- glmmTMB(indiv_pull ~ OT*csi  + 
                    #OT*related + OT*z.rank_diff_abs +
                    (1|subject) + (1|recipient),
                zi = ~1,
                family = nbinom2, data = accessible.data)

summary(ZINB_2)

Anova(ZINB_2, type = 3)

tab_model(ZINB_2,
          show.est = TRUE, show.ci = 0.95,
          show.p = TRUE, p.style = "numeric",
          show.se = TRUE, show.r2 = TRUE,
          show.zeroinf = FALSE,
          show.re.var = FALSE, show.icc = FALSE,
          transform = NULL,
          title = "ZINB Regression Predicting the Number of Prosocial Lever Pulls")
```


```{r Model 2: QuasiPoisson What factors influence prosocial pulls?}
# Quasi-Poisson Regression
QUASI2 <- glmmTMB(indiv_pull ~ OT*z.csi  +
                    (1|subject) + (1|recipient),
                zi = ~1,
                family = nbinom1, data = accessible.data)

summary(QUASI2)

Anova(QUASI2, type = 3)

tab_model(QUASI2,
          show.est = TRUE, show.ci = 0.95,
          show.p = TRUE, p.style = "numeric",
          show.se = TRUE, show.r2 = TRUE,
          show.zeroinf = FALSE,
          show.re.var = FALSE, show.icc = FALSE,
          transform = NULL,
          title = "QuasiPoisson Regression Predicting the Number of Prosocial Lever Pulls")

anova(ZINB_2, QUASI2, test = "chisq")
# Quasi-Poisson was a better model with AIC = 4591.1 compared to AIC = 4839.8 
# Chi Sq value = 248.66 p<0.001



```

```{r Re-Run Model 2 with Runs Removed}

accessible.data$pull_minus_run <- (accessible.data$indiv_pull - accessible.data$indiv_run)

# Quasi-Poisson Regression
QUASI_NoRuns <- glmmTMB(pull_minus_run ~ OT*z.csi +
                    (1|subject) + (1|recipient),
                zi = ~1,
                family = nbinom1, data = accessible.data)

summary(QUASI_NoRuns)

Anova(QUASI_NoRuns, type = 3)

tab_model(QUASI_NoRuns,
          show.est = TRUE, show.ci = 0.95,
          show.p = TRUE, p.style = "numeric",
          show.se = TRUE, show.r2 = TRUE,
          show.zeroinf = FALSE,
          show.re.var = FALSE, show.icc = FALSE,
          transform = NULL,
          title = "Quassi Poisson Regression Predicting the Number of Prosocial Lever Pulls w/o runs")

anova(QUASI_NoRuns, QUASI2, test = "chisq")
```

```{r}
QUASI2_RANK <- glmmTMB(indiv_pull ~ OT*z.rank_diff_abs +
                    (1|subject) + (1|recipient),
                zi = ~1,
                family = nbinom1, data = accessible.data)

summary(QUASI2_RANK)

Anova(QUASI2_RANK, type = 3)

tab_model(QUASI2_RANK,
          show.est = TRUE, show.ci = 0.95,
          show.p = TRUE, p.style = "numeric",
          show.se = TRUE, show.r2 = TRUE,
          show.zeroinf = FALSE,
          show.re.var = FALSE, show.icc = FALSE,
          transform = NULL,
          title = "QuasiPoisson Regression Predicting the Number of Prosocial Lever Pulls")

anova(QUASI2_RANK, QUASI2, test = "chisq")
```

```{r Re-run the Model 2 but include rank (despite colinearity)}
# Quasi-Poisson Regression
QUASI_withRank <- glmmTMB(indiv_pull ~ OT*z.csi + 
                            OT*z.rank_diff_abs + 
                            z.rank_diff_abs*z.csi +
                    (1|subject) + (1|recipient),
                zi = ~1,
                family = nbinom1, data = accessible.data)

summary(QUASI_withRank)

Anova(QUASI_withRank, type = 3)

tab_model(QUASI_withRank,
          show.est = TRUE, show.ci = 0.95,
          show.p = TRUE, p.style = "numeric",
          show.se = TRUE, show.r2 = TRUE,
          show.zeroinf = FALSE,
          show.re.var = FALSE, show.icc = FALSE,
          transform = NULL,
          title = "QuasiPoiss Regression Predicting the Number of Prosocial Lever Pulls")

anova(QUASI_withRank, QUASI2, test = "chisq")

```



```{r Compare to a Random Effects only Model}
random_effects_only <- glmmTMB(indiv_pull ~ (1|subject) + (1|recipient),
               zi = ~1,
               family = nbinom1, data = accessible.data)

summary(random_effects_only)

anova(QUASI2, random_effects_only, test = "chisq")

##

random_effects_only_no_run <- glmmTMB(pull_minus_run ~ (1|subject) + (1|recipient),
               zi = ~1,
               family = nbinom1, data = accessible.data)

summary(random_effects_only_no_run)

anova(random_effects_only_no_run, QUASI_NoRuns, test = "chisq")
```
