---
title: "Group Prosociality with OT"
output: word_document
date: "2022-09-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Install your Packages}
#install.packages("rstudioapi")
#install.packages("openxlsx")
#install.packages("dplyr")
#install.packages("tidyr")
#install.packages("tidyverse")
#install.packages("pscl")
#install.packages("multcomp")
#install.packages("lsmeans")
#install.packages("fitdistrplus")
#install.packages("glmmTMB")
#install.packages("overdisp")
#install.packages("sjPlot")
#install.packages("Rmisc")
#install.packages("rstatix")
#install.packages("MASS")
#install.packages("gridExtra")
#install.packages("grid")
#install.packages("gridtext")

```

```{r Library your Packages}
library(rstudioapi)
library(openxlsx)
library(readxl)
library(dplyr)
library(tidyr)
library(tidyverse)
library(pscl)
library(multcomp)
library(emmeans)
library(lsmeans)
library(fitdistrplus)
library(lme4)
library(car)
library(glmmTMB)
library(emmeans)
library(overdisp)
library(sjPlot)
library(rstatix)
library(MASS)
library(gridExtra)
library(grid)
library(gridtext)

```


```{r Read the Data File}

model5.data <- read_excel("C:/Users/matth/OneDrive/Documents/Georgia State/Research Projects/Group Prosociality/Data Collection and Schedule/Final Results and Final R Code/Model_3_Data_Reciprocity.xlsx")

```

```{r Clean the Data Frames}
model5.data$session_number <- as.numeric(model5.data$session_number)
model5.data$subjecta <- as.factor(model5.data$subjecta)
model5.data$subjectb <- as.factor(model5.data$subjectb)
model5.data$unique_id <- as.factor(model5.data$unique_id)
model5.data$pulls_a_to_b <- as.numeric(model5.data$pulls_a_to_b)
model5.data$pulls_b_to_a <- as.numeric(model5.data$pulls_b_to_a)
model5.data$sex_a <- as.factor(model5.data$sex_a)
model5.data$sex_b <- as.factor(model5.data$sex_b)
model5.data$age_a <- as.numeric(model5.data$age_a)
model5.data$age_b <- as.numeric(model5.data$age_b)
model5.data$rank_a <- as.numeric(model5.data$rank_a)
model5.data$rank_b <- as.numeric(model5.data$rank_b)
model5.data$rank_score_a <- as.numeric(model5.data$rank_score_a)
model5.data$rank_score_b <- as.numeric(model5.data$rank_score_b)
model5.data$group <- as.factor(model5.data$group)
model5.data$rank_diff <- as.numeric(model5.data$rank_diff)
model5.data$sex_pair <- as.factor(model5.data$sex_pair)
model5.data$avg_csi <- as.numeric(model5.data$avg_csi)

levels(model5.data$subjecta)
levels(model5.data$subjectb)
summary(model5.data$a_to_b)
summary(model5.data$b_to_a)

```

```{r Visualize Reciprocity}

reciprocity.data <- read_excel("C:/Users/matth/OneDrive/Documents/Georgia State/Research Projects/Group Prosociality/Data Collection and Schedule/Final Results and Final R Code/Reciprocity Data/reciprocity_data.xlsx")

```

```{r Visualize by Dyad}
library(plyr)
library(Rmisc)

# group.rec data is formed from the following code:
# accessible.data <- subset(model2.data, session_type == "Accessible)
# logan.data <- subset(accessible.data, group == "logan")
# logan.rec <- summarySE(logan.data, measurevar="indiv_pull", groupvars=c("dyad_idx", "session_number"))
# logan.rec <- logan.rec %>%
#  mutate(a_or_b = if_else(grepl("a", dyad_idx), "a", "b"),
#         dyad_num = as.numeric(gsub("[^0-9]", "", dyad_idx)))

logan.rec <- read_excel("C:/Users/matth/OneDrive/Documents/Georgia State/Research Projects/Group Prosociality/Data Collection and Schedule/Final Results and Final R Code/Reciprocity Data/logan_rec.xlsx")

by.dyad.logan <- summarySE(logan.rec, measurevar = "indiv_pull", groupvars = c("dyad_num", "a_or_b"))

by.dyad.logan$indiv_pull <- ifelse(by.dyad.logan$a_or_b == "b", -by.dyad.logan$indiv_pull, by.dyad.logan$indiv_pull)

griffin.rec <- read_excel("C:/Users/matth/OneDrive/Documents/Georgia State/Research Projects/Group Prosociality/Data Collection and Schedule/Final Results and Final R Code/Reciprocity Data/griffin_rec.xlsx")

by.dyad.griffin <- summarySE(griffin.rec, measurevar = "indiv_pull", groupvars = c("dyad_num", "a_or_b"))

by.dyad.griffin$indiv_pull <- ifelse(by.dyad.griffin$a_or_b == "b", -by.dyad.griffin$indiv_pull, by.dyad.griffin$indiv_pull)

nkima.rec <- read_excel("C:/Users/matth/OneDrive/Documents/Georgia State/Research Projects/Group Prosociality/Data Collection and Schedule/Final Results and Final R Code/Reciprocity Data/nkima_rec.xlsx")

by.dyad.nkima <- summarySE(nkima.rec, measurevar = "indiv_pull", groupvars = c("dyad_num", "a_or_b"))

by.dyad.nkima$indiv_pull <- ifelse(by.dyad.nkima$a_or_b == "b", -by.dyad.nkima$indiv_pull, by.dyad.nkima$indiv_pull)

mason.rec <- read_excel("C:/Users/matth/OneDrive/Documents/Georgia State/Research Projects/Group Prosociality/Data Collection and Schedule/Final Results and Final R Code/Reciprocity Data/mason_rec.xlsx")

by.dyad.mason <- summarySE(mason.rec, measurevar = "indiv_pull", groupvars = c("dyad_num", "a_or_b"))

by.dyad.mason$indiv_pull <- ifelse(by.dyad.mason$a_or_b == "b", -by.dyad.mason$indiv_pull, by.dyad.mason$indiv_pull)
```


```{r Visualize by Dyad}
logan_pull_graph <- ggplot(by.dyad.logan, aes(x=dyad_num, 
                                              y = indiv_pull,
                                              ymin = indiv_pull - ci,
                                              ymax = indiv_pull + ci,
                                              fill = a_or_b)) +
  geom_bar(stat = "identity", position = "identity") +
  geom_errorbar(position = "identity", width=0.4, colour="black", alpha=0.9, size=1.0) +
  scale_fill_manual(values = c("lightgreen", "darkgreen"), name = "", labels = c("Presses favor Subordinate", "Presses favor Dominant")) +
  labs(title = "Group 1 (n = 6)", x = "Dyads", y = "Average lever presses per session") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_blank(),
        axis.title = element_text(size = 14),
        legend.position = "none",
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank()) +  # Adjust axis text size
  coord_flip() +  # Flip coordinates for horizontal bars
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  ylim(-30, 30)

griffin_pull_graph <- ggplot(by.dyad.griffin, aes(x=dyad_num, y = indiv_pull,
                                              ymin = indiv_pull - ci,
                                              ymax = indiv_pull + ci,
                                              fill = a_or_b)) +
  geom_bar(stat = "identity", position = "identity") +
  geom_errorbar(position = "identity", width=0.4, colour="black", alpha=0.9, size=1.0) +
  scale_fill_manual(values = c("lightgreen", "darkgreen"), name = "", labels = c("Presses favor Subordinate", "Presses favor Dominant")) +
  labs(title = "Group 2 (n = 5)", x = "Dyads", y = "Average lever presses per session") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_blank(),
        axis.title = element_text(size = 14),
        legend.position = "none",
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank()) +  # Adjust axis text size
  coord_flip() +  # Flip coordinates for horizontal bars
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  ylim(-30, 30)


nkima_pull_graph <- ggplot(by.dyad.nkima, aes(x=dyad_num, y = indiv_pull,
                                              ymin = indiv_pull - ci,
                                              ymax = indiv_pull + ci,
                                              fill = a_or_b)) +
  geom_bar(stat = "identity", position = "identity") +
  geom_errorbar(position = "identity", width=0.4, colour="black", alpha=0.9, size=1.0) +
  scale_fill_manual(values = c("lightgreen", "darkgreen"), name = "", labels = c("Presses favor Subordinate", "Presses favor Dominant")) +
  labs(title = "Group 3 (n = 4)", x = "Dyads", y = "Average lever presses per session") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_blank(),
        axis.title = element_text(size = 14),
        legend.position = "none",
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank()) +  # Adjust axis text size
  coord_flip() +  # Flip coordinates for horizontal bars
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  ylim(-30, 30)


by.dyad.mason.no.zero <- subset(by.dyad.mason, indiv_pull != 0.00)

by.dyad.mason.no.zero$dyad_num_new <- by.dyad.mason.no.zero$dyad_num

by.dyad.mason.no.zero$dyad_num_new <- ifelse(by.dyad.mason.no.zero$dyad_num_new == 8, 5, 
                                             ifelse(by.dyad.mason.no.zero$dyad_num_new == 14, 6, 
                                                    ifelse(by.dyad.mason.no.zero$dyad_num_new == 15, 7,
                                                           ifelse(by.dyad.mason.no.zero$dyad_num_new == 16, 8,
                                                                  ifelse(by.dyad.mason.no.zero$dyad_num_new == 19, 9,
                                                                  ifelse(by.dyad.mason.no.zero$dyad_num_new == 20, 10,
                                                                         ifelse(by.dyad.mason.no.zero$dyad_num_new == 22, 11,
                                                                                ifelse(by.dyad.mason.no.zero$dyad_num_new == 23, 12,
                                                                                       ifelse(by.dyad.mason.no.zero$dyad_num_new == 24, 13,
                                                                                              ifelse(by.dyad.mason.no.zero$dyad_num_new == 25, 14,
                                                                                                     by.dyad.mason.no.zero$dyad_num_new))))))))))


mason_pull_graph <- ggplot(by.dyad.mason.no.zero, aes(x=dyad_num_new, y = indiv_pull,
                                              ymin = indiv_pull - ci,
                                              ymax = indiv_pull + ci,
                                              fill = a_or_b)) +
  geom_bar(stat = "identity", position = "identity") +
  geom_errorbar(position = "identity", width=0.4, colour="black", alpha=0.9, size=1.0) +
  scale_fill_manual(values = c("lightgreen", "darkgreen"), name = "", labels = c("Presses favor Subordinate", "Presses favor Dominant")) +
  labs(title = "Group 4 (n = 8)", x = "Dyads", y = "Average lever presses per session") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_blank(),
        axis.title = element_text(size = 14),
        legend.position = "none",
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank()) +  # Adjust axis text size
  coord_flip() +  # Flip coordinates for horizontal bars
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  ylim(-30, 30)

logan_pull_graph
griffin_pull_graph
nkima_pull_graph
mason_pull_graph

g_reciprocity<-grid.arrange(logan_pull_graph, griffin_pull_graph, nkima_pull_graph, mason_pull_graph, 
                nrow = 2)

ggsave("Reciprocity_per_sessions.png", g_reciprocity, height = 6, width = 8, units = "in")

rm(logan_pull_graph, griffin_pull_graph, nkima_pull_graph, mason_pull_graph)

rm(by.dyad.griffin, by.dyad.logan, by.dyad.mason, by.dyad.nkima, by.dyad.mason.no.zero)

```


```{r Run a correlation between A to B and B to A}
# Remove the pulls where there was a 0, because there is no contingent short term reciprocity if one pair is never pulling
reciprocity.data.no.zero <- subset(reciprocity.data, a_to_b != 0)

cor.test(reciprocity.data.no.zero$a_to_b, reciprocity.data.no.zero$b_to_a, method = c("pearson"))
```
It seems that there was a non-significant NEGATIVE correlation, indicating that within each session, as Pulls from A to B increased, Pulls from B to A decreased. However, it is possible that there is general reciprocity going on. Maybe Individual A pulls more during sessions in which they also recieved a lot of pulls themselves, independent of who pulled for them. Of course, this could be due to a number of reasons/intentions, but lets investigate if it was happening.

GENERALIZED RECIPROCITY - MODEL 4 ------------------------------------------------------------------------------------------------------------------------------

```{r Now Check if there was General Reciprocity. Independent of dyads.}
# Attach the data frame that is broken down by each subject, the number of pulls they recieved and the number of pulls they donated per session
general.rec <- read_excel("C:/Users/matth/OneDrive/Documents/Georgia State/Research Projects/Group Prosociality/Data Collection and Schedule/Final Results and Final R Code/Reciprocity Data/Pulls_and_Recieves_per_Session_per_Subject.xlsx")

# First a simple correlation:
# A significant negative correlation! Wow so even generally, the more one receives the less likely they are to pull
cor.test(general.rec$rec_sum, general.rec$pull_sum, method = c("pearson"))

# Now a correlation where all the sessions in which a subject did not recieve pulls are removed
# Still a significant negative correlation
general.rec2 <- subset(general.rec, rec_sum != 0)
cor.test(general.rec2$rec_sum, general.rec2$pull_sum, method = c("pearson"))

rm(general.rec2)
```


```{r Now Visualize the General Reciprocity}
general.recip.rec <- summarySE(general.rec, measurevar = "rec_sum", groupvars = "subject")
general.recip.rec$give_or_rec <- "Receive"
general.recip.rec$rec_sum <- -general.recip.rec$rec_sum

general.recip.give <- summarySE(general.rec, measurevar = "pull_sum", groupvars = "subject")
general.recip.give$give_or_rec <- "Give"

colnames(general.recip.rec)[3] <- "avg_pulls"
colnames(general.recip.give)[3] <- "avg_pulls"

general.recip.visual <- rbind(general.recip.rec, general.recip.give)

general_pull_graph <- ggplot(general.recip.visual, aes(x=subject, 
                                                       y = avg_pulls,
                                              ymin = avg_pulls - ci,
                                              ymax = avg_pulls + ci,
                                              fill = give_or_rec)) +
  geom_bar(stat = "identity", position = "identity") +
  geom_errorbar(position = "identity", width=0.4, colour="black", alpha=0.9, size=1.0) +
  scale_fill_manual(values = c("lightgreen", "darkgreen"), name = "", labels = c("Given", "Received")) +
  labs(x = "Subject", y = "Average lever presses per session") +
  theme_bw() +
  theme(axis.text.x = element_text(size = 20),
        axis.text.y = element_blank(),
        legend.position = "none",
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.title = element_text(size = 25)) +  # Adjust axis text size
  coord_flip() +  # Flip coordinates for horizontal bars
  geom_hline(yintercept = 0, linetype = "solid", color = "black") +
  ylim(-50, 50)

general_pull_graph

ggsave("General_Reciprocity_Graph.png", height = 10, width = 15, units = "in")

```

```{r GLMM Analysis to Determine if Reciprocity was occurring}
head(model5.data)
# Response Variable
summary(model5.data$pulls_a_to_b)

# Check for over dispersion
# Over dispersion occurs when the Variance of your DV is >>> Mean of your DV
var(model5.data$pulls_a_to_b)
mean(model5.data$pulls_a_to_b)

# Variance Ratio = 17.018
var(model5.data$pulls_a_to_b)/mean(model5.data$pulls_a_to_b)
# Over dispersion = PRESENT!
```
Mean: 0.693
Variance: 11.79
Variance Ratio: 17.018

HUGE OVERDISPERSION means we need Negative Binomial or Quasi-Poisson


```{r Correlation between CSI and Rank Difference}
# Correlation between CSI and Rank
model5.data$rank_diff_abs <- abs(model5.data$rank_diff)

ggplot(model5.data, aes(x = rank_diff_abs, y = avg_csi)) +
  geom_point() +
  geom_smooth(method = lm) +
  theme_classic()

cor.test(model5.data$avg_csi, model5.data$rank_diff_abs, method = "pearson")
```

```{r ZINB [NOT USED] Model 3: Short Term Contigent Reciprocity within Dyad within Session}
# Negative Binomial Regression
ZINB_5 <- glmmTMB(pulls_a_to_b ~ pulls_b_to_a + rank_diff +
                  (1 + pulls_b_to_a | subjecta) + (1 + pulls_b_to_a | subjectb) + (1 + pulls_b_to_a | unique_id),
                zi = ~1,
                family = nbinom2, data = model5.data)

# The model does NOT converge: Error in eigen(h) : infinite or missing values in 'x'
```


```{r ZINB [NOT USED] Model 3: Short Term Contigent Reciprocity within Dyad within Session}
ZINB_5 <- glmmTMB(pulls_a_to_b ~ pulls_b_to_a + rank_diff +
                  (1 + pulls_b_to_a | subjecta) + (1 + pulls_b_to_a | subjectb),
                zi = ~1,
                family = nbinom2, data = model5.data)


summary(ZINB_5)

Anova(ZINB_5, type = 3)

tab_model(ZINB_5,
          show.est = TRUE, show.ci = 0.95,
          show.p = TRUE, p.style = "numeric",
          show.se = TRUE, show.r2 = TRUE,
          show.zeroinf = FALSE,
          show.re.var = FALSE, show.icc = FALSE,
          transform = NULL,
          title = "ZINB Regression Predicting the Number of Prosocial Lever Pulls")
```


```{r ZIP Model 3: Short Term Contigent Reciprocity within Dyad within Session}
# Quasi-Poisson Regression
QUASI_5 <- glmmTMB(pulls_a_to_b ~ pulls_b_to_a + rank_diff +
                  (1 + pulls_b_to_a | subjecta) + (1 + pulls_b_to_a | subjectb) + (1 + pulls_b_to_a | unique_id),
                zi = ~1,
                family = nbinom1, data = model5.data)

# The model does NOT converge: Error in eigen(h) : infinite or missing values in 'x'

QUASI_5 <- glmmTMB(pulls_a_to_b ~ pulls_b_to_a + rank_diff +
                  (1 + pulls_b_to_a | subjecta) + (1 + pulls_b_to_a | subjectb),
                zi = ~1,
                family = nbinom1, data = model5.data)

# This model also does NOT converge, try again:
QUASI_5 <- glmmTMB(pulls_a_to_b ~ pulls_b_to_a + rank_diff +
                  (1 | subjecta) + (1 + pulls_b_to_a | subjectb),
                zi = ~1,
                family = nbinom1, data = model5.data)

# This model also does NOT converge, try again:
QUASI_5 <- glmmTMB(pulls_a_to_b ~ pulls_b_to_a + rank_diff +
                  (1 | subjecta) + (1 | subjectb),
                zi = ~1,
                family = nbinom1, data = model5.data)

# This model converges! yay...
QUASI_5 <- glmmTMB(pulls_a_to_b ~ pulls_b_to_a +
                  (1 | subjecta) + (1 | subjectb) + (1 | unique_id),
                zi = ~1,
                family = nbinom1, data = model5.data)



summary(QUASI_5)

Anova(QUASI_5, type = 3)

tab_model(QUASI_5,
          show.est = TRUE, show.ci = 0.95,
          show.p = TRUE, p.style = "numeric",
          show.se = TRUE, show.r2 = TRUE,
          show.zeroinf = FALSE,
          show.re.var = FALSE, show.icc = FALSE,
          transform = NULL,
          title = "QuasiPoisson Regression Predicting the Number of Prosocial Lever Pulls")


```

```{r Model 4: ZIP Model for Generalized Reciprocity within each Session}
# This model does not converge
QUASI_6 <- glmmTMB(pull_sum ~ rec_sum*rank_score +
                  (1 + rec_sum| subject),
                zi = ~1,
                family = nbinom1, data = general.rec)

# This model converges
QUASI_6 <- glmmTMB(pull_sum ~ rec_sum*rank_score +
                  (1 | subject),
                zi = ~1,
                family = nbinom1, data = general.rec)

summary(QUASI_6)

  Anova(QUASI_6, type = 3)

tab_model(QUASI_6,
          show.est = TRUE, show.ci = 0.95,
          show.p = TRUE, p.style = "numeric",
          show.se = TRUE, show.r2 = TRUE,
          show.zeroinf = FALSE,
          show.re.var = FALSE, show.icc = FALSE,
          transform = NULL,
          title = "ZINB Regression Predicting the Number of Prosocial Lever Pulls")

```


```{r Compare both models to a random_effects only model}
Null5 <- glmmTMB(pulls_a_to_b ~ (1 | subjecta) + (1 | subjectb) + (1 | unique_id),
                zi = ~1,
                family = nbinom1, data = model5.data)

Null6 <- glmmTMB(pull_sum ~ (1 | subject),
                zi = ~1,
                family = nbinom1, data = general.rec)


anova(Null5, QUASI_5, test = "chisq")

anova(Null6, QUASI_6, test = "chisq")

```

Model 3 did not show signficant improvement from null model
Model 4 did
