---
title: "Group Prosociality with OT"
output: word_document
date: "2022-09-19"
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
```

```{r Install your Packages}
#install.packages("rstudioapi")
#install.packages("openxlsx")
#install.packages("dplyr")
#install.packages("tidyr")
#install.packages("tidyverse")
#install.packages("pscl")
#install.packages("multcomp")
#install.packages("lsmeans")
#install.packages("fitdistrplus")
#install.packages("glmmTMB")
#install.packages("overdisp")
#install.packages("sjPlot")
#install.packages("Rmisc")
#install.packages("rstatix")
#install.packages("MASS")
```

```{r Library your Packages}
library(rstudioapi)
library(openxlsx)
library(readxl)
library(dplyr)
library(tidyr)
library(tidyverse)
library(pscl)
library(multcomp)
library(emmeans)
library(lsmeans)
library(fitdistrplus)
library(lme4)
library(car)
library(glmmTMB)
library(emmeans)
library(overdisp)
library(sjPlot)
library(rstatix)
library(MASS)
```

```{r Read the Data File}

model3.data <- read_excel("C:/Users/matth/OneDrive/Documents/Georgia State/Research Projects/Group Prosociality/Data Collection and Schedule/Final Results and Final R Code/Model_5_Data_Frame.xlsx")

group_dictionary <- read_excel("C:/Users/matth/OneDrive/Documents/Georgia State/Research Projects/Group Prosociality/Data Collection and Schedule/Final Results and Final R Code/Group Dictionary.xlsx")

recipient.demographics <- read_excel("C:/Users/matth/OneDrive/Documents/Georgia State/Research Projects/Group Prosociality/Data Collection and Schedule/Final Results and Final R Code/Recipient_Demographics.xlsx")

proximity.demographics <- read_excel("C:/Users/matth/OneDrive/Documents/Georgia State/Research Projects/Group Prosociality/Data Collection and Schedule/Final Results and Final R Code/Proximity_Demographics.xlsx")

demographics <- read_excel("C:/Users/matth/OneDrive/Documents/Georgia State/Research Projects/Group Prosociality/Data Collection and Schedule/Final Results and Final R Code/Monkey_Demographics2.xlsx")

merged.data <- merge(x = model3.data, y = group_dictionary, by.x = "donor", by.y = "subject")
merged.data <- merged.data[, -which(names(merged.data) == "rank.y")]
merged.data <- merged.data[, -which(names(merged.data) == "rank_score.y")]
colnames(merged.data)[colnames(merged.data) == "rank.x"] <- "rank"
colnames(merged.data)[colnames(merged.data) == "rank_score.x"] <- "rank_score"

head(merged.data)
model3.data <- merged.data

rm(group_dictionary, merged.data)

```

```{r Clean the Data Frames}

model3.data$time <- as.numeric(model3.data$time)
model3.data$session_number <- as.numeric(model3.data$session_number)
model3.data$session_type <- as.factor(model3.data$session_type)
model3.data$pull_number <- as.numeric(model3.data$pull_number)
model3.data$donor <- as.factor(model3.data$donor)
summary(model3.data$donor)
model3.data$rank <- as.numeric(model3.data$rank)
model3.data$recipient_y_n <- as.factor(model3.data$recipient_y_n)
model3.data$recipient <- as.factor(model3.data$recipient)
model3.data$proximity_y_n <- as.factor(model3.data$proximity_y_n)
model3.data$proximity_a <- as.factor(model3.data$proximity_a)
model3.data$proximity_b <- as.factor(model3.data$proximity_b)
model3.data$aggression <- as.factor(model3.data$aggression)
model3.data$run <- as.factor(model3.data$run)
model3.data$OT <- as.factor(model3.data$OT)
model3.data$rank_score <- as.numeric(model3.data$rank_score)
model3.data$group <- as.factor(model3.data$group)

levels(model3.data$donor)
levels(model3.data$session_type)
levels(model3.data$aggression)
levels(model3.data$run)
levels(model3.data$OT)
levels(model3.data$recipient_y_n)
levels(model3.data$proximity_y_n)

# Reorder the data frame to have a chronological order of the pulls
model3.data <- model3.data %>% 
  arrange(group, session_number, time)

# Now form the previous_donor column, shifting the "donor" column down 1
model3.data <- model3.data %>%
  mutate(previous_donor = lag(donor))

# Now calculate the number of seconds that elapsed since the previous pull was made
model3.data <- model3.data %>%
  mutate(time_since_last_pull = time - lag(time))

#write.csv(model3.data, file = "Model_6_Data_Edited.csv", row.names = FALSE)

```

```{r For Model 5, we are interested in Runs, but those only occur in Accessible Sessions }
accessible.data <- subset(model3.data, session_type == "Accessible")
summary(accessible.data$session_type)

# Number of Runs
nrow(subset(accessible.data, run == 1))
# Number of Aggressions
nrow(subset(accessible.data, aggression == 1))


```

Total Pulls in the Accessible Sessions: 4933

Total Pulls with at least 1 recipient: 3398

Total Pulls with no recipient: 1534

Total Pulls followed by a Run: 2562

Total Pulls followed by an Aggression: 103

```{r Descriptives}
run.data <- subset(accessible.data, run == 1)
# Number of runs when no one was there:
nrow(subset(run.data, recipient_y_n == 0 & proximity_y_n == 0))
# Number of Runs when recipient was there, but no one in prox
nrow(subset(run.data, recipient_y_n == 1 & proximity_y_n == 0))
# Number of Runs when there was a monkey in prox but did not receive juice
nrow(subset(run.data, recipient_y_n == 0 & proximity_y_n == 1))
# Number of runs when there was at least 2 monkeys near the fountain, one of which received
nrow(subset(run.data, recipient_y_n == 1 & proximity_y_n == 1))

no.run.data <- subset(accessible.data, run == 0)
# Number of runs when no one was there:
nrow(subset(no.run.data, recipient_y_n == 0 & proximity_y_n == 0))
# Number of Runs when recipient was there, but no one in prox
nrow(subset(no.run.data, recipient_y_n == 1 & proximity_y_n == 0))
# Number of Runs when there was a monkey in prox but did not receive juice
nrow(subset(no.run.data, recipient_y_n == 0 & proximity_y_n == 1))
# Number of runs when there was at least 2 monkeys near the fountain, one of which received
nrow(subset(no.run.data, recipient_y_n == 1 & proximity_y_n == 1))

nrow(subset(run.data, recipient_y_n == 1))
nrow(subset(no.run.data, recipient_y_n == 1))

# Calculate Proportions
(nrow(subset(run.data, recipient_y_n == 0 & proximity_y_n == 0))) / (nrow(subset(no.run.data, recipient_y_n == 0 & proximity_y_n == 0)) + nrow(subset(run.data, recipient_y_n == 0 & proximity_y_n == 0)))

(nrow(subset(run.data, recipient_y_n == 1 & proximity_y_n == 0))) / (nrow(subset(no.run.data, recipient_y_n == 1 & proximity_y_n == 0)) + nrow(subset(run.data, recipient_y_n == 1 & proximity_y_n == 0)))

(nrow(subset(run.data, recipient_y_n == 0 & proximity_y_n == 1))) / (nrow(subset(no.run.data, recipient_y_n == 0 & proximity_y_n == 1)) + nrow(subset(run.data, recipient_y_n == 0 & proximity_y_n == 1)))

(nrow(subset(run.data, recipient_y_n == 1 & proximity_y_n == 1))) / (nrow(subset(no.run.data, recipient_y_n == 1 & proximity_y_n == 1)) + nrow(subset(run.data, recipient_y_n == 1 & proximity_y_n == 1)))
```
# Number of runs when no one was there: 880
# Number of NO RUNs when no one was there: 662
# Proportion of Runs: 0.57

# Number of runs whith a recipient but no one else was there: 1223
# Number of NO RUNs whith a recipient but no one else was there: 1118
# Proportion of Runs: 0.52

# Number of Runs when there was a monkey in prox but did not receive juice: 146
# Number of NO RUNs when there was a monkey in prox but did not receive juice: 140
# Proportion of Runs: 0.51

# Number of runs when there was at least 2 monkeys near the fountain, one of which received: 313
# Number of NO RUNs when there was at least 2 monkeys near the fountain, one of which received: 451
# Proportion of Runs: 0.41

```{r}
accessible.data$rec_or_prox <- ifelse(accessible.data$recipient_y_n == 0 & accessible.data$proximity_y_n == 0, 0, 1)

detach("package:Rmisc")
detach("package:plyr")

session_run_counts <- accessible.data %>%
  group_by(donor, session_number, rec_or_prox) %>%  # Group by donor, session_number, and rec_or_prox
  summarize(
    runs = sum(run == 1),                             # Count of `run == 1`
    no_runs = sum(run == 0),                          # Count of `run == 0`
    .groups = "drop"                                  # Ungroup after summarizing
  ) %>%
  # Ensure that all combinations of donor, session_number, and rec_or_prox are present
  complete(donor, session_number, rec_or_prox, fill = list(runs = 0, no_runs = 0))

# Sort the data frame by donor (alphabetically) and then by session_number (ascending)
session_run_counts <- session_run_counts %>%
  arrange(donor, session_number)

temp_demogr <- subset(demographics, select = c("subject", "group", "rank_cat"))

session.run.counts <- merge(session_run_counts, temp_demogr, by.x = "donor", by.y = "subject")

session.run.counts <- subset(session.run.counts, select = c("donor", "group", "rank_cat", "session_number", "rec_or_prox", "runs", "no_runs"))

session.run.counts$total_runs <- (session.run.counts$runs + session.run.counts$no_runs)

session.run.counts <- session.run.counts %>%
  mutate(
    run_prop = ifelse(is.nan(runs / total_runs), 0, runs / total_runs)  # Replace NaN with 0
  )

# Logan's Group: Remove 12, 14, 19, 21, 26, 28, 33, 35
logan.runs <- subset(session.run.counts, group == "logan")
logan.runs <- logan.runs %>%
  filter(!session_number %in% c(12, 14, 19, 21, 26, 28, 33, 35))

griffin.runs <- subset(session.run.counts, group == "griffin")
griffin.runs <- griffin.runs %>%
  filter(!session_number %in% c(12, 14, 19, 21, 26, 28, 33, 35))


nkima.runs <- subset(session.run.counts, group == "nkima")
nkima.runs <- nkima.runs %>%
  filter(!session_number %in% c(13, 15, 20, 22, 27, 29, 34, 36))


mason.runs <- subset(session.run.counts, group == "mason")
mason.runs <- mason.runs %>%
  filter(!session_number %in% c(12, 16, 19, 23, 26, 30, 33, 37))

session.run.counts <- rbind(logan.runs, griffin.runs, nkima.runs, mason.runs)

rm(temp_demogr, session_run_counts, logan.runs, griffin.runs, nkima.runs, mason.runs)

library(plyr)
library(Rmisc)

session.run.summary <- summarySE(session.run.counts, measurevar = "run_prop", groupvars = c("rank_cat", "rec_or_prox"))
session.run.summary$rank_cat <- as.factor(session.run.summary$rank_cat)
session.run.summary$rec_or_prox <- as.factor(session.run.summary$rec_or_prox)


```


```{r}

significance_data <- data.frame(
  rank_cat = c("1", "2", "3", "4"),        # Category labels
    rec_or_prox = c("0", "1", "0", "1"), # Corresponding to rec_or_prox
   y_position = c(0.80, 0.65, 0.65, 0.40),    # Position for the significance labels
  label = c("**", "***", "***", "***"),     # Significance labels
  xmin = c(0.8, 1.8, 2.8, 3.8),            # Starting x positions for the horizontal lines
  xmax = c(1.2, 2.2, 3.2, 4.2)             # Ending x positions for the horizontal lines
)


Figure_5 <- ggplot(session.run.summary, aes(x = rank_cat, y = run_prop, fill = rec_or_prox)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = run_prop - ci, ymax = run_prop + ci),
                position = position_dodge(0.9), width = 0.2) +
  geom_text(data = significance_data, aes(x = rank_cat, y = y_position, label = label), 
            size = 6, color = "black", fontface = "bold") +
  geom_segment(data = significance_data,
               aes(x = xmin, xend = xmax, y = y_position - 0.02, yend = y_position - 0.02),
               color = "black", size = 0.6) +
  theme_bw() +
  labs(x = "Rank Category", y = "Proportion of Presses followed by a run") +
  scale_fill_manual(values = c("0" = "darkgreen", "1" = "lightgreen"), labels = c("No Recipient", "Recipient Present")) +
  scale_x_discrete(labels = c("1" = "Alpha Males", "2" = "Alpha Females", "3" = "Beta Females", "4" = "Subordinates")) +
  coord_cartesian(ylim = c(0, 1)) +
  theme(axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 10),
        axis.title.y = element_text(size = 16),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.position = c(0.80, 0.85),
        )

Figure_5

ggsave("C:/Users/matth/OneDrive/Documents/Georgia State/Research Projects/Group Prosociality/MANUSCRIPT/Figure_5.png", height = 5, width = 8)
```



```{r Make the Dataframe for Visualization of Counts}
no.recipient <- subset(accessible.data, recipient_y_n == 0 & proximity_y_n == 0)
table(no.recipient$donor, no.recipient$run)
temp1 <- data.frame(table(no.recipient$donor, no.recipient$run))
no.run.temp <- subset(temp1, Var2 == 0)
run.temp <- subset(temp1, Var2 == 1)
no.recipient <- merge(no.run.temp, run.temp, by.x = "Var1", by.y = "Var1")
no.recipient$rec <- 0
no.recipient$prox <- 0
no.recipient$rec_or_prox_var <- 0

prox.no.recipient <- subset(accessible.data, recipient_y_n == 0 & proximity_y_n == 1)
table(prox.no.recipient$donor, prox.no.recipient$run)
temp1 <- data.frame(table(prox.no.recipient$donor, prox.no.recipient$run))
no.run.temp <- subset(temp1, Var2 == 0)
run.temp <- subset(temp1, Var2 == 1)
prox.no.recipient <- merge(no.run.temp, run.temp, by.x = "Var1", by.y = "Var1")
prox.no.recipient$rec <- 0
prox.no.recipient$prox <- 1
prox.no.recipient$rec_or_prox_var <- 1
  
recipient.no.prox <- subset(accessible.data, recipient_y_n == 1 & proximity_y_n == 0)
table(recipient.no.prox$donor, recipient.no.prox$run)
temp1 <- data.frame(table(recipient.no.prox$donor, recipient.no.prox$run))
no.run.temp <- subset(temp1, Var2 == 0)
run.temp <- subset(temp1, Var2 == 1)
recipient.no.prox <- merge(no.run.temp, run.temp, by.x = "Var1", by.y = "Var1")
recipient.no.prox$rec <- 1
recipient.no.prox$prox <- 0
recipient.no.prox$rec_or_prox_var <- 1

recipient.and.prox <- subset(accessible.data, recipient_y_n == 1 & proximity_y_n == 1)
table(recipient.and.prox$donor, recipient.and.prox$run)
temp1 <- data.frame(table(recipient.and.prox$donor, recipient.and.prox$run))
no.run.temp <- subset(temp1, Var2 == 0)
run.temp <- subset(temp1, Var2 == 1)
recipient.and.prox <- merge(no.run.temp, run.temp, by.x = "Var1", by.y = "Var1")
recipient.and.prox$rec <- 1
recipient.and.prox$prox <- 1
recipient.and.prox$rec_or_prox_var <- 1

recipient.at.all <- subset(accessible.data, recipient_y_n == 1 | proximity_y_n == 1)
table(recipient.at.all$donor, recipient.at.all$run)
temp1 <- data.frame(table(recipient.at.all$donor, recipient.at.all$run))
no.run.temp <- subset(temp1, Var2 == 0)
run.temp <- subset(temp1, Var2 == 1)
recipient.at.all <- merge(no.run.temp, run.temp, by.x = "Var1", by.y = "Var1")
recipient.at.all$rec_or_prox_var <- 1

runs.by.donor <- rbind(no.recipient, recipient.no.prox, prox.no.recipient, recipient.and.prox)
colnames(runs.by.donor)[1] = "donor"
colnames(runs.by.donor)[3] = "no_run"
colnames(runs.by.donor)[5] = "run"

no.rec.temp <- subset(no.recipient, select = c(1:5, 8))
runs.by.donor.simplified <- rbind(no.rec.temp, recipient.at.all)
rm(no.rec.temp)
colnames(runs.by.donor.simplified)[1] = "donor"
colnames(runs.by.donor.simplified)[3] = "no_run"
colnames(runs.by.donor.simplified)[5] = "run"

runs.by.donor <- subset(runs.by.donor, select = c(1,3,5,6,7,8))
runs.by.donor.simplified <- subset(runs.by.donor.simplified, select = c(1,3,5,6))


runs.by.donor$runs_per_session = (runs.by.donor$run)/30
runs.by.donor$no_runs_per_session = (runs.by.donor$no_run)/30
runs.by.donor.simplified$runs_per_session = (runs.by.donor.simplified$run)/30
runs.by.donor.simplified$no_runs_per_session = (runs.by.donor.simplified$no_run)/30

runs.by.donor$donor <- as.factor(runs.by.donor$donor)
runs.by.donor$rec <- as.factor(runs.by.donor$rec)
runs.by.donor.simplified$donor <- as.factor(runs.by.donor.simplified$donor)
runs.by.donor.simplified$rec_or_prox_var <- as.factor(runs.by.donor.simplified$rec_or_prox_var)


runs.by.donor$run_prop <- ((runs.by.donor$run)/(runs.by.donor$run + runs.by.donor$no_run))
runs.by.donor.simplified$run_prop <- ((runs.by.donor.simplified$run)/(runs.by.donor.simplified$run + runs.by.donor.simplified$no_run))

runs.by.donor[is.na(runs.by.donor)] <- 0
runs.by.donor.simplified[is.na(runs.by.donor.simplified)] <- 0

rm(no.recipient, recipient.no.prox, prox.no.recipient, recipient.and.prox, temp1, no.run.temp, run.temp)
```

```{r}

```


```{r Visualize Runs by Recipient/Proximity}
# Use this for bargraphs
library(plyr)
library(Rmisc)
runs.by.donor$rec_or_prox_var <- ifelse(runs.by.donor$rec == 0 & runs.by.donor$prox == 0, 0, 1)


```


```{r}
demographics <- read_excel("C:/Users/matth/OneDrive/Documents/Georgia State/Research Projects/Group Prosociality/Data Collection and Schedule/Final Results and Final R Code/Monkey_Demographics2.xlsx")

merged.data <- merge(x = demographics, y = runs.by.donor, by.x = "subject", by.y = "donor")
nrow(merged.data) == nrow(merged.data)
head(merged.data)
runs.by.donor <- merged.data

Run_by_Rank_Graph <- ggplot(runs.by.donor, aes(x = rank, y = run_prop, color = rec)) +
  geom_point() +
  geom_jitter(width = 0.5, height = 0) +
  geom_smooth(aes(color = rec), method = glm, se=FALSE, fullrange=FALSE, level = 0.95) +
  #facet_wrap(~rec) +
  theme_bw() +
  labs(x = "Rank (Elo Rating)", y = "Proportion of pulls followed by a run") +
  scale_color_manual(values = c("0" = "red", "1" = "purple4"), labels = c("No Recipient", "Recipient Present")) +
  theme(axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 10),
        axis.title.y = element_text(size = 16),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.position = c(0.85, 0.85),
        )

Run_by_Rank_Graph
#ggsave("run_by_rank_graph.png", height = 5, width = 8, units = "in")
```


```{r}
rank.cat.data <- runs.by.donor
rank.cat.data <- subset(rank.cat.data, select = c("subject", "sex", "age", "rank", "rank_score", "group", "no_run", "run", "rec", "prox"))
rank.cat.data$rec_or_prox <- ifelse(rank.cat.data$rec == 0 & rank.cat.data$prox == 0, 0, 1)

detach("package:Rmisc")
detach("package:plyr")
rank.cat.data2 <- rank.cat.data %>%
  group_by(subject, rec_or_prox) %>%
  summarise(run_rec = sum(run), no_run_rec = sum(no_run)) %>%
  ungroup()
library(plyr)
library(Rmisc)

rank.cat.data2$runs_per_session = (rank.cat.data2$run_rec)/30
rank.cat.data2$no_runs_per_session = (rank.cat.data2$no_run_rec)/30

rank.cat.data2$subject <- as.factor(rank.cat.data2$subject)
rank.cat.data2$rec_or_prox <- as.factor(rank.cat.data2$rec_or_prox)
rank.cat.data2$run_prop <- ((rank.cat.data2$run_rec)/(rank.cat.data2$run_rec + rank.cat.data2$no_run_rec))
rank.cat.data2$run_prop[is.nan(rank.cat.data2$run_prop)] <- 0.00
rank.cat.data.merged <- merge(x = demographics, y = rank.cat.data2, by.x = "subject", by.y = "subject")

rank.cat.data.merged$rank_cat <- ifelse(rank.cat.data.merged$rank_score == 1, 1, 4)
rank.cat.data.merged$rank_cat <- ifelse(rank.cat.data.merged$subject == "Ivory" | rank.cat.data.merged$subject == "Lexi" | rank.cat.data.merged$subject == "Gambit" | rank.cat.data.merged$subject == "Scarlett", 2, rank.cat.data.merged$rank_cat)
rank.cat.data.merged$rank_cat <- ifelse(rank.cat.data.merged$subject == "Ira" | rank.cat.data.merged$subject == "Lily" | rank.cat.data.merged$subject == "Nala" | rank.cat.data.merged$subject == "Beeker", 3, rank.cat.data.merged$rank_cat)

rank.cat.data.merged$rank_cat <- as.factor(rank.cat.data.merged$rank_cat)


df_runs_by_rank_cat <- summarySE(rank.cat.data.merged, measurevar = "run_prop", groupvars = c("rank_cat", "rec_or_prox"))


```

```{r Divided By Subject}
alpha_male_df <- subset(rank.cat.data.merged, rank_cat == 1)

alpha_male_run_graph <- ggplot(alpha_male_df, aes(x = subject, y = run_prop, fill = rec_or_prox)) +
  geom_bar(stat = "identity", position = "dodge") +
  #facet_wrap(~rec) +
  theme_bw() +
  labs(x = "Subject", y = "Proportion of Presses followed by a run") +
  scale_fill_manual(values = c("0" = "darkgreen", "1" = "lightgreen"), labels = c("No Recipient", "Recipient Present")) +
  ylim(0, 1) +
  theme(axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 10),
        axis.title.y = element_text(size = 16),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.position = "none",
        )
alpha_male_run_graph

#--------------------------------------------------------------------------------------------------------------------------------------

alpha_female_df <- subset(rank.cat.data.merged, rank_cat == 2)

alpha_female_run_graph <- ggplot(alpha_female_df, aes(x = subject, y = run_prop, fill = rec_or_prox)) +
  geom_bar(stat = "identity", position = "dodge") +
  #facet_wrap(~rec) +
  theme_bw() +
  labs(x = "Subject", y = "Proportion of Presses followed by a run") +
  scale_fill_manual(values = c("0" = "darkgreen", "1" = "lightgreen"), labels = c("No Recipient", "Recipient Present")) +
  ylim(0, 1) +
  theme(axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 10),
        axis.title.y = element_text(size = 16),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.position = c(0.85, 0.85),
        )
alpha_female_run_graph

# ----------------------------------------------------------------------------------------------------------------------------
beta_female_df <- subset(rank.cat.data.merged, rank_cat == 3)

beta_female_run_graph <- ggplot(beta_female_df, aes(x = subject, y = run_prop, fill = rec_or_prox)) +
  geom_bar(stat = "identity", position = "dodge") +
  #facet_wrap(~rec) +
  theme_bw() +
  labs(x = "Subject", y = "Proportion of Presses followed by a run") +
  scale_fill_manual(values = c("0" = "darkgreen", "1" = "lightgreen"), labels = c("No Recipient", "Recipient Present")) +
  ylim(0, 1) +
  theme(axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 10),
        axis.title.y = element_text(size = 16),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.position = "none",
        )
beta_female_run_graph

#-------------------------------------------------------------------------------------------------------------------------------------

subordinate_df <- subset(rank.cat.data.merged, rank_cat == 4)

subordinate_run_graph <- ggplot(subordinate_df, aes(x = subject, y = run_prop, fill = rec_or_prox)) +
  geom_bar(stat = "identity", position = "dodge") +
  #facet_wrap(~rec) +
  theme_bw() +
  labs(x = "Subject", y = "Proportion of Presses followed by a run") +
  scale_fill_manual(values = c("0" = "darkgreen", "1" = "lightgreen"), labels = c("No Recipient", "Recipient Present")) +
  ylim(0, 1) +
  theme(axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 10),
        axis.title.y = element_text(size = 16),
        legend.title = element_blank(),
        legend.text = element_text(size = 12),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.position = "none",
        )
subordinate_run_graph

rm(alpha_male_df, alpha_female_df, beta_female_df, subordinate_df)

library(gridExtra)
g_rank_run <- grid.arrange(alpha_male_run_graph, alpha_female_run_graph, beta_female_run_graph, subordinate_run_graph,
                nrow = 2)

```

```{r Z-center if needed, and make sure Rank is Categorical}
# Z center numeric variables
accessible.data$z.rank = as.vector(scale(accessible.data$rank))
accessible.data$z.pull_number = as.vector(scale(accessible.data$pull_number))

accessible.data$rec_or_prox <- ifelse(accessible.data$recipient_y_n == 0 & accessible.data$proximity_y_n == 0, 0, 1)

accessible.data$rank_cat <- ifelse(accessible.data$rank_score == 1, 1, 4)
accessible.data$rank_cat <- ifelse(accessible.data$donor == "Ivory" | accessible.data$donor == "Lexi" | accessible.data$donor == "Gambit" | accessible.data$donor == "Scarlett", 2, accessible.data$rank_cat)
accessible.data$rank_cat <- ifelse(accessible.data$donor == "Ira" | accessible.data$donor == "Lily" | accessible.data$donor == "Nala" | accessible.data$donor == "Beeker", 3, accessible.data$rank_cat)

accessible.data$rank_cat <- as.factor(accessible.data$rank_cat)
```

```{r Test for Colinearity with VIF}
simple_model1 <- lm(as.numeric(run) ~ OT + pull_number + rec_or_prox + rank_cat, data = accessible.data)

summary(simple_model1)

vif(simple_model1)

# ALL VIFs should be low, around 1.0 preferably Above 2.5 is concerning

# Rank and Sex should be high because they are colinear together
```

```{r Run the Model}
Model_5 <- glmer(run ~  OT + pull_number + rec_or_prox*rank_cat +
                  (1|donor), 
                 family = binomial(link='logit'), 
                 data = accessible.data,
                 control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun = 10000)))

summary(Model_5)

Anova(Model_5, type = 3)

tab_model(Model_5,
          show.est = TRUE, show.ci = 0.95,
          show.p = TRUE, p.style = "numeric",
          show.se = TRUE, show.r2 = TRUE,
          show.zeroinf = FALSE,
          show.re.var = FALSE, show.icc = FALSE,
          title = "Logistic Regression Predicting the Likelihood of Running after a Pull")
```


```{r Probe Significant Interaction}
# First, calculate the estimated marginal means (EMMs) for the interaction
emm <- emmeans(Model_5, ~ rec_or_prox * rank_cat)

# Perform pairwise comparisons within each level of rank_cat (0 vs 1 for rec_or_prox)
emm_contrasts <- contrast(emm, method = "revpairwise", adjust = "bonferroni")

# Print the results of the pairwise comparisons
summary(emm_contrasts)
```

contrast                                        estimate     SE  df z.ratio p.value
rec_or_prox1 rank_cat1 - rec_or_prox0 rank_cat1   0.3772 0.0983 Inf   3.836  0.0031
rec_or_prox1 rank_cat2 - rec_or_prox0 rank_cat2  -1.9933 0.2691 Inf  -7.408  <.0001
rec_or_prox1 rank_cat3 - rec_or_prox0 rank_cat3  -1.6941 0.1438 Inf -11.780  <.0001
rec_or_prox1 rank_cat4 - rec_or_prox0 rank_cat4  -3.8370 0.5625 Inf  -6.822  <.0001

Negative value means that running was higher without a recipient than  with recipient
Positive value means that running was higher with recipient than without a recipient (Alpha Males)



```{r Null Model Comparison}
# Random Effects only
random_effects_only <- glmer(run ~  (1|donor), 
                 family = binomial(link='logit'), 
                 data = accessible.data,
                 control = glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun = 10000)))

# bobyqa = optimizer To avoid a warning of nonconvergence

summary(random_effects_only)

# Compare the 2 models
anova(random_effects_only, Model_5, test = "chisq")

```


```{r How well does your model classify the data?}
# Next set up a confusion matrix, which is a technique used in machine learning to test how well your model predicts your data. 

# Run the test data through the model
res <- predict(Model_5, accessible.data, type = "response")

# Set up a confusion matrix to validate the model
conf_matrix <- table(Actual_Value = accessible.data$run, Predicted_Value = res > 0.5)
conf_matrix

# What percent of cases in your data were predicted accurately (as a case or non-case) given your model:
(conf_matrix[[1,1]] + conf_matrix[[2,2]]) / sum(conf_matrix)

# 68.8% Correct Prediction of Cases
```
```{r Check Model Stability}
source("glmm_stability.r")
m.stab=glmm.model.stab(model.res=Model_5)
#m.stab.plot(m.stab$summary[, -1])
round(m.stab$summary[, -1], 3)
m.stab.plot <- round(m.stab$summary[, -1], 3)
m.stab.plot$variables <- row.names(m.stab.plot)
m.stab.plot <- subset(m.stab.plot, variables != "(Intercept)")
m.stab.plot <- subset(m.stab.plot, variables != "donor@(Intercept)@NA")

ggplot(m.stab.plot, aes(x = variables, y = orig)) +
  geom_pointrange(aes(ymin = min, ymax = max)) +
  geom_hline(yintercept = 0.0, size = 1, linetype = "solid") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))

```






